Stable Neo-Hookean Flesh Simulation

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
now at eigenanalysis..... no cannot do

If the energy had rest stability $P_{D}(I)$ would resolve to zero. Unfortunately this is not the case here. In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$:
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}
\]
therefore resulting to:
\[
P_{E}(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right]
\]
\[
= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F)
\]
Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$.

\subsection{Lamé Reparametrization}

\subsection{Previous Work}
\todoredefined[inline]{
TODO: Here comes previous work in neo-hookean energy formulation. What is neo-hookean and why do we need it here?
And what is wrong with each one.
}

\subsection{Stable Neo-Hookean Energy}
Conclude to the energy proposed in the paper.

\section{Energy Analysis}
Calculations and Herleitungen

>>>>

If the energy had rest stability $P_{D}(I)$ would resolve to zero. Unfortunately this is not the case here. In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$:
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}
\]
therefore resulting to:
\[
P_{E}(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right]
\]
\[
= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F)
\]
Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2}
\]
\[
= \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}
\]
Since constant disappear under differentiation this expression is functionally equivalent to 
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2}.
\]
Now one can notice that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$. The difference is that we replaced $log(J)$ with $(J-1)$ in $\Psi_{E}$. Remember that $(J-1)$ is the first term in the taylor approximation of $log(J)$ at $J=1$.

\todoredefined[inline]{
TODO: Add "Zwischenschritte"? Include all calculations? Do we need a bit of a better conclusion of what we did (taylor, neo, sing. free, rest stable)?
}

\subsection{Meta-Stability under Degeneracy}
The final energy is
\begin{equation}\label{eq:stable_energy}
\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right).
\end{equation}
With that adjustment the rest stability term shifts to $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.

\todoredefined[inline]{
TODO: How much needs to be explained here?
}

\subsection{Lamé Reparametrization}
\todoredefined[inline]{
TODO: How much needs to be explained here?
}

\section{Energy Analysis}
In this chapter it is shown that one can perform a complete eigenanalysis on equation \ref{eq:stable_energy}.
